Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 0127

%%----Versions-----------------------------
% supCLT0124.tex 2018/01/24 by Jianjie
% supCLT0109.tex 2018/01/14 by Yanxia
% supCLT0107.tex 2018/01/07 by Jianjie
% supclt1231.tex 2018/12/14 by Zhenyao
% supclt1213.tex 2018/12/14 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt,a4paper]{amsart}
	\setlength{\textwidth}{\paperwidth}
	\addtolength{\textwidth}{-2in}
	\calclayout
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
	\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage[backref=section]{hyperref}
	\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
	\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{comment}
\usepackage{amsthm}
	\theoremstyle{plain}
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lem}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem{cor}[thm]{Corollary}
	\newtheorem{conj}[thm]{Conjecture}
	\theoremstyle{definition}
	\newtheorem{defi}[thm]{Definition}
	\newtheorem{rem}[thm]{Remark}
	\newtheorem{exa}[thm]{Example}
	\newtheorem{asp}{Assumption}
	\numberwithin{equation}{section}
	\allowdisplaybreaks
%\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

@@

   According to  Subsection A.1, the branching mechanism $\psi$ can be extended to
    $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
 \[\psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb C_+,\]
    which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
    \quad z\in \mathbb C^0_+.
\end{equation}
{ \bf
\begin{asp}
\label{asp: branching mechanism}
    The branching mechanism takes the form of
\[
    \psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
\]
    where $\eta > 0$, $\gamma \in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
\[
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
\]
\end{asp}
\begin{lem}
    Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
    Also, $\psi$ satisfies the $L \log L$ critierion  i.e.
\[
    \int_1^\infty y \log y~\pi(dr)< \infty.
\]
\end{lem}
\begin{proof}
    { Need a proof.}
\end{proof}
}
    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\bar v \|\mu\|},
\end{equation}
    where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define
\begin{equation}\label{meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}
 %new added
 In this paper, we will establish some spatial central limit theorems for the super-OU process with stable branching mechanism. Precisely, we want to find $F_t$ and $G_t$ such that
 $$\frac{\langle f, X_t \rangle -G_t}{F_t}$$ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition.

 There are many papers studying central limit behavior for branching processes, branching diffusions and superprocesses. See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes under some certain conditions. In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a forth moment condition. In this two paper, Milo\'s with his coauthor pictured connection between CLT and what they call branching rate regimes. In \cite{RSZ}, Yanxia Ren, Renming Song and Rui Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. Moverover, Compare with the results in \cite{ARMP,MP2012}, the limit distributions in \cite{RSZ} are non-degenerate. In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.

 All the results described above hold for systems with branching mechanisms satisfying finite variance. It's a natural step to establish counterparts of the central limit theorems for super processes with infinite variance.  In \cite{MM}, Marks and Milo\'s have considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. They established some central limit theorems on the small and critical branching rate cases but no large rate case. In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. On small and critical branching cases, we obtained similar central limit theorems. Moreover, on large rate case, we not only show an almost sure convergent result, but also establish the corresponding central limit theorem, which is not appeared in \cite{MM}.

 Except for the main results proved in section 4, there are some other significative results in our paper. In appendix, we show that the characteristic exponent of supercritical general super processes $U_t f(x)=-{\rm Log} \mathbb{P}_{\delta_x}e^{i\theta X_t(f)}$ can be defined by corresponding equation by using Spain Decomposition. In section 3, we establish a small value probability estimation of supercritical continuous-state branching processes with branching mechanism satisfying Grey's condition and $L\log L$ critierion. This all results are necessary for us to prove the central limit theorems.

 % end new
\subsection{OU Semigroup}
    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb R^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
     For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
    let $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    p \in \mathbb{Z}_+^{d}.
\end{equation}
    It is known that $(P_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
    discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\begin{equation}
    \mathcal{A}_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    P_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    Thus, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
\end{equation}
    the order of the function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb R^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
\subsection{Main Results}
We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all
finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of super-OU process.
In this subsection, we will give the main results of this paper.
\subsubsection{Large branching rate}

@@

\subsection{h-controller  for super-OU process.}
Let $X$ be the super-OU process introduced in Subsection 1.1. Write $\psi_0(z)=\psi(z)+\alpha z$, for each $z\in \mathbb{C}_+$, and define operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$ by
\begin{equation}\begin{split}
    \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x)
    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big),
    \quad  f\in \mathcal B(\mathbb R^d, \mathbb C_+), x\in \mathbb R^d.
\end{split}\end{equation}
For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
%the value of the L\'evy exponent of the infinite divisible random variable
the value of the characteristic exponent of the infinite divisible random variable
$\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{equation}\begin{split}
\label{eq:chareq2}
    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
    =i P^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
\end{split}\end{equation}
If let
\begin{equation}\begin{split}
\label{eq: def of Zf}
    Z_t f
    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
    \\ Z'_t f
    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,
    \\ Z''_t f
    &:= \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
    \\ K_t f
    &:= (Z'_t - Z_t+ Z''_t)f,
\end{split}\end{equation}
    Then we have that
\[
    U_t - i P^\alpha_t
    = Z'_t + Z''_t
    = Z_t+ (Z'_t - Z_t) + Z''_t
    = Z_t+K_t, \quad t\geq 0.
\]

@@

Further, for each $f\in \mathcal{P}$ satisfying $\alpha\beta<\kappa_fb(1+\beta)$,
According to \eqref{domi-m}, $\sum_{k=0}^\infty |m_k[f]|<\infty$, and  then
\begin{equation}\label{sum-m}
m[f]
    :=\sum_{k=0}^\infty m_k[f]
    =\int_0^{\infty} e^{-\alpha s} \langle \eta (-iP_s^\alpha f)^{1+\beta}, \varphi \rangle~ds.
% new added
% I move ahead the follow lemma used in prop 2.6.

@@

\section{Tail probability}
In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and %control
$(1+\gamma)$-moments for the super-OU process. These will be needed to prove our main results.

>>>>

%%----Versions-----------------------------
% supCLT0127.tex 2018/01/27 by Yanxia
% supCLT0124.tex 2018/01/24 by Jianjie
% supCLT0114.tex 2018/01/14 by Yanxia
% supCLT0107.tex 2018/01/07 by Jianjie
% supclt1231.tex 2018/12/14 by Zhenyao
% supclt1213.tex 2018/12/14 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt,a4paper]{amsart}
	\setlength{\textwidth}{\paperwidth}
	\addtolength{\textwidth}{-2in}
	\calclayout
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
	\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage[backref=section]{hyperref}
	\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
	\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{comment}
\usepackage{amsthm}
	\theoremstyle{plain}
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lem}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem{cor}[thm]{Corollary}
	\newtheorem{conj}[thm]{Conjecture}
	\theoremstyle{definition}
	\newtheorem{defi}[thm]{Definition}
	\newtheorem{rem}[thm]{Remark}
	\newtheorem{exa}[thm]{Example}
	\newtheorem{asp}{Assumption}
	\numberwithin{equation}{section}
	\allowdisplaybreaks
%\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

@@

   According to  Subsection A.1, the branching mechanism $\psi$ can be extended to
    $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
 \[\psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb C_+,\]
    which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
    \quad z\in \mathbb C^0_+.
\end{equation}
{ \bf
\begin{asp}
\label{asp: branching mechanism}
    The branching mechanism takes the form of
\[
    \psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
\]
    where $\eta > 0$, $\gamma \in (0,1)$ and that there exists $C >0$ and $\delta >0$ such that
\[
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
\]
\end{asp}
\begin{lem}
    Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
    Also, $\psi$ satisfies the $L \log L$ critierion  i.e.
\[
    \int_1^\infty y \log y~\pi(dr)< \infty.
\]
\end{lem}
\begin{proof}
    { Need a proof.}
\end{proof}
}
    According to \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\bar v \|\mu\|},
\end{equation}
    where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define
\begin{equation}\label{meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}

 In this paper, we will establish some spatial central limit theorems for the super-OU process with stable branching mechanism. Precisely, we want to find $F_t$ and $G_t$ such that
 $$\frac{\langle f, X_t \rangle -G_t}{F_t}$$ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition.

 There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes under some certain conditions. In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a forth moment condition. In this two paper, Milo\'s with his coauthor pictured connection between CLT and what they call branching rate regimes. In \cite{RSZ}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. Moverover, Compare with the results in \cite{ARMP,MP2012}, the limit distributions in \cite{RSZ} are non-degenerate. In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.

 All the results described above hold for systems with branching mechanisms satisfying finite variance. It's a natural  to ask that how to establish counterparts of the central limit theorems for branching Markov processes and superprocesses with infinite variance.  In \cite{MM}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. They established some central limit theorems for small and critical branching rate cases,  but leave the central limit result unsolved for large rate case. In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. For small and critical branching cases, we obtained central limit theorems which are similar to corresponding results for branching Ornstein-Uhlenbeck processes in Marks and Milo\'s \cite{MM}. For large rate case, we first establish  an almost sure convergent result, and then establish a central limit theorem, which has no corresponds in \cite{MM}.

 %Except for the main results proved in section 4, there are some other significative results in our paper. In appendix, we show that the characteristic exponent of supercritical general super processes $U_t f(x)=-{\rm Log} \mathbb{P}_{\delta_x}e^{i\theta X_t(f)}$ can be defined by corresponding equation by using Spain Decomposition. In section 3, we establish a small value probability estimation of supercritical continuous-state branching processes with branching mechanism satisfying Grey's condition and $L\log L$ critierion. This all results are necessary for us to prove the central limit theorems.

\subsection{OU Semigroup}
    In this subsection, we recall some results on the spectral properties of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb R^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb R^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$. $L^2(\varphi)$ is a Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb Z_+ := \mathbb N\cup\{0\}$.
     For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$,
    let $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d,
    p \in \mathbb{Z}_+^{d}.
\end{equation}
    It is known that $(P_t)$ is a strongly continuous semigroup on $L^2(\varphi)$ and $L$ has
    discrete spectrum $a(L)= \{-bk: k \in \mathbb Z_+\}$.
    For each $k \in \mathbb Z_+$, denote by $\mathcal{A}_k$ the eigenspace corresponding to the eigenvalue $-bk$, then
\begin{equation}
    \mathcal{A}_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb Z_+^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{a}x \Big),
    \quad x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    P_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb R^d, p\in \mathbb Z_+^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    Thus, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \},
\end{equation}
    the order of the function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb R^d):\exists~ C>0, n \in \mathbb Z_+, {\rm ~s.t.~} \forall x\in \mathbb R^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
\subsection{Main Results}
We will use $\mathcal M_c(\mathbb R^d)$ to denote the space of all
finite Borel measures of compact support on $\mathbb R^d$ and $D$ to denote the extinction event of super-OU process.
In this subsection, we will give the main results of this paper.
\subsubsection{Large branching rate}

@@

\subsection{h-controller  for super-OU process.}
Let $X$ be the super-OU process introduced in Subsection 1.1. Write $\psi_0(z)=\psi(z)+\alpha z$, for each $z\in \mathbb{C}_+$, and define operators on $\mathcal{B}(\mathbb{R}^d,\mathbb{C}_+)$ by
\begin{equation}\begin{split}
    \Psi f (x) &:= -\alpha f(x) + \eta f(x)^{1+\beta} + \psi_1\big(f(x)\big),
    \\\Psi_0 f(x) &:= \Psi f(x) + \alpha f(x)
    \\ \Psi_1 f(x) &:= \psi_1 \big(f(x)\big),
    \quad  f\in \mathcal B(\mathbb R^d, \mathbb C_+), x\in \mathbb R^d.
\end{split}\end{equation}
For all $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, recall that $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$,
the value of the characteristic exponent of the infinite divisible random variable
$\langle f, X_t\rangle$ at $1$.
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ takes values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{equation}\begin{split}
\label{eq:chareq2}
    U_tf(x)-\int_0^t P^\alpha_{t-s} \Psi_0(-U_sf)(x)ds
    =i P^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in \mathbb{R}^d, f\in \mathcal P.
\end{split}\end{equation}
If let
\begin{equation}\begin{split}
\label{eq: def of Zf}
    Z_t f
    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)ds,
    \\ Z'_t f
    &:= \int_0^t P^\alpha_{t-s}\big( \eta (-U_s f)^{1+\beta}\big)ds,
    \\ Z''_t f
    &:= \int_0^t P^\alpha_{t-s}\Psi_1(-U_s f)ds,
    \\ K_t f
    &:= (Z'_t - Z_t+ Z''_t)f,
\end{split}\end{equation}
    Then we have that
\[
    U_t - i P^\alpha_t
    = Z'_t + Z''_t
    = Z_t+ (Z'_t - Z_t) + Z''_t
    = Z_t+K_t, \quad t\geq 0.
\]

@@

%moved from below
\begin{lem}\label{lem: control of gk}(\cite[Lemma 2.8]{MM})
    For each $f\in \mathcal{P}$, let
    \begin{align}
        g_k
    := \frac{Z_1 P^{\alpha}_k f-\langle  Z_1P^{\alpha}_k f,\varphi\rangle}{e^{(\alpha-\kappa_f b)(1+\beta)t}},
    \quad k \geq 0.
    \end{align}
    There exist $h\in \mathcal{P}$ such that
    \begin{align}
        |P_sg_k|\leq e^{-bs}h,\quad s\geq 0, k \geq 0.
    \end{align}
\end{lem}
% end move
%moved from below
\begin{lem}\label{control of gn} Suppose that $g\in \mathcal{C}_l$.
    Put
    \begin{align}
        \bar{g}_t:=\frac{Z_1(-I_tg)-\langle Z_1(-I_tg),\varphi\rangle}{e^{-(\alpha-Kb)(1+\beta)t}},\quad t\geq 0.
    \end{align}
    There exists $h\in \mathcal{P}$ such that
    \begin{align}
        |P_s\bar{g}_t|\leq e^{-bs}h,\quad s\geq 0, t\geq 0.
    \end{align}
\end{lem}
\begin{proof}
    The proof  is similar to that of \cite[Lemma 2.8]{MM}.
\end{proof}
% end move

@@

\section{Tail probability}
In this section, we will introduce a small value probability result of supercritical continuous-state branching process with general branching mechanism and
$(1+\gamma)$-moments for the super-OU process. These will be needed to prove our main results.
